Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-08 README.Rmd
added an image
worked on updating the readme

This repository contains the files associated with the paper "Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations" by Katherine Goode and Heike Hofmann. The rest of this readme contains information about the files in the repository, instructions for knitting the paper, descriptions of the bullet data used in the paper, and information on the font sizes used for the figures in the manuscript.

@@

- `figure-static` contains the figures in the paper that are not generated by R.
- `old-version` contains the files associated with an old version of the paper that is much longer the the submitted version.
- `submission` contains all of the files submitted to the ASA data science journal.
  - Note that the paper is specified slightly different in this folder in order to meet the requirements of the ASA data science journal. For example, the figure path in the .Rnw saves the generated figures in the main folder (instead of a figures folder), and the paths in the .Rnw file are different. It also contains additional files such as data (whereas the data used by the .Rnw file in the main folder is stored elsewhere).

@@

- `.gitignore` contains objects to be ignored by git.
- `paper.Rnw` and `paper.pdf` are the manuscript.
- `references.bib` contains the bibtex information for the 
- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA data science journal.

@@

**Note**: When the paper is knit, various files will be generated (such as data-bullet-explain.rds and figure-10-1.png). The first time the paper is knit, it will take approximately an hour to run. Once these files have been generated during the first knit, the paper will take much less time to knit (approximately 1 minute).

@@

1. Pull the repository from GitHub.
2. Unzip all .zip files in the repository (data-bullet-train.csv.zip, data-bullet-test.csv.zip, data-example-signatures.csv.zip, and figure-08-1.png.zip).
3. Install R packages goodekat/lime and goodekat/limeaid R from GitHub using devtools.

@@

### Steps for Preparing Submission Folder

>>>>

```{r echo = FALSE}
knitr::include_graphics("figure-readme.png")
```

This repository contains the files associated with the paper "Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations" by Katherine Goode and Heike Hofmann. The rest of this readme contains:

- information about the files in the repository,
- instructions for knitting the paper,
- descriptions of the bullet data used in the paper, 
- information on the font sizes used for the figures in the manuscript, 
- and the steps taken to create the `submission` folder.

@@

- `old-version` contains the files associated with an old version of the paper that is much longer the the submitted version.
- `submission` contains all of the files submitted to the ASA data science journal. Note that the paper is specified slightly different in this folder in order to meet the requirements of the ASA data science journal. These are as follows:
  - The figure path in the .Rnw saves the generated figures in the main folder (instead of a figures folder).

@@

- `code-file-organization.R` contains R code for organizing the files to be added to the GitHub repository and generating a file with code for submission.
- `code-paper.R` contains the R code extracted from `paper.Rnw` using code in `code-file-organization.R`.
- `data-bullet-test.csv.zip` and `data-bullet-test.csv.zip` contain the data used for the bullet examples in the paper. Additional information about these files is included below under the heading "Additional Information on Bullet Data".
- `data-example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- **`data-no-tank-rash.csv.zip` is a temporary fix file and needs to be deleted eventually!!!!**
- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
- `.gitignore` contains objects to be ignored by git.
- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
- `README.Rmd` and `README.md` are the readme files that generated this output. :)
- `references.bib` contains the bibtex information for the 
- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA data science journal.

@@

When the paper is knit, various files will be generated (such as `data-bullet-explain.rds` and `figure-10-1.png`). The first time the paper is knit, it will take a while (approximately 45 minutes on Katherine's computer). Once these files have been generated during the first knit, the paper will take much less time to knit (approximately 1 minute on Katherine's computer).

@@

1. Pull the repository from GitHub.
2. Unzip all .zip files in the repository (`data-bullet-train.csv.zip`, `data-bullet-test.csv.zip`, `data-example-signatures.csv.zip`, **`data-no-tank-rash.csv.zip`**, and `figure-08-1.png.zip`).
3. Install R packages goodekat/lime and goodekat/limeaid R from GitHub using devtools.

@@

### Steps Followed to Create the Submission Folder
